Messaging Architecture for Integration of Customer Self Service Systems \\ Version 0.1

### 2020-09-28 expose/main.tex
add info on how problems are solved

Resources and especially time are scarce. Integration therefore has to be as simple and fast as possible.
Simple means e.g. that existing systems do not need to be modified for integration or, 
that integration systems do not differ fundamentally between heterogenious landscapes.

Of course, besides being simple and fast, it also has to enable EA and business connector to access each others 
functionalities according to their requirements.

@@

The bachelor thesis defines a messaging architecture for integration of CSS systems into existing enterprise
architectures.

@@

An integration architecture gets defined, which utilizes the selected business processes, architecture 
bricks and data objects in order to integrate the business connector. Purpose of the integration is to enable 
the EA and business connector to access each others functionalities according to their requirements considering 
the rigid and heterogenious nature of the EA. Rather technological requirements like scalability and fail safety 
and possible solutions will be evaluated while creating the integration architecture.
Architecture bricks and data objects used in the final form of the 
integration architecture can be seen as its requirements towards the existing EA.

>>>>

Resources and especially time are scarce. Integration therefore needs to be as simple and fast as possible and 
function with little support, failure and modification over time. The variety of heterogenious landscapes and their constant 
development make this challenging. The integration has to interface with an EA without the need of changing it but also be able to 
adabt to its modifications.
Of course, the integration also has to perform according to requirements of both the EA and the CSS business connector, which 
the bachelor thesis evaluates.
As an integration does not only interface with systems but also delivers information and instructions, additional requirements 
relating to reliability e.g. sclability, failure safety have to be considered.

@@

In order to simplify integration, the bachelor thesis defines a messaging architecture for integration of a CSS connector 
into enterprise
architectures. The integration architecture simplifies integration by providing a integration solution reusable in many different 
scenarios. It uses a messaging approach to be applicaple to heterogenious landscapes through loosely coupling. 
Loose coupling allows integrated systems to not make assumptions about each other and use a send-and-forget approach, 
simplifying their integration.
Messaging systems can also reliably handle communication through e.g load balancing and store-and-forward mechanisms.
If the integration system satisifes requirements of the EA and business connector will be validated on a real life example.
An operation manual presented by the thesis aims to further reduce deployment time and complexity and is used in the evaluation.

The following describes the planned approaches:

@@

An integration architecture gets defined, which utilizes the selected business processes, architecture 
bricks and data objects in order to integrate the business connector. Purpose of the integration is to enable 
the EA and business connector to access each others functionalities according to their requirements.
Requirements relating to the internal data and instruction delivery like e.g. scalability and fail safety will be considered.
Architecture bricks and data objects used in the final form of the 
integration architecture can be seen as its requirements towards the existing EA.
